QPLIB: A Library of Quadratic Programming Instances

### 2018-08-08 QPLIB-3.tex
Update QPLIB-3.tex

\begin{table}
\textcolor{red}{
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{llr}
\toprule
Variables & Convexity & \#\\
\cmidrule(lr){1-3}
%
 \textit{continuous}	& \textit{convex}		&  32 \\[1.2 ex]
 \textit{continuous}	& \textit{nonconvex} 	&  102 \\[1.2 ex]
 \textit{discrete}	& \textit{convex}		&  31 \\[1.2 ex]
 \textit{discrete}	& \textit{nonconvex}	&  288 \\[1.2 ex]
\cmidrule(lr){1-3}
Total		&				& 453\\
%
\bottomrule
\end{tabular}
\caption{Macro classification of the final set of instances}
\label{tab:DDDDD}
}
\end{table}

 The detailed characteristics of the instances are presented in Table
\ref{tab:DD} for \emph{discrete} instances
(\textit{*}\{\textit{B,M,I,G}\}\textit{*}) and in Table
\ref{tab:CC} for \emph{continuous} ones (\textit{*C*}).
For each category, the tables
report in column ``$\#$'' the corresponding number of instances. It can be seen
that the final set well respects the original distribution of the gathered
instances among the different categories. Indeed, the discrete categories
\textit{LMQ} and \textit{QBL} are well represented by \textcolor{red}{134} and \textcolor{red}{91}
instances, respectively. Similarly, the continuous categories
\textit{LCQ} and \textit{QCQ} are well
represented by \textcolor{red}{52} and \textcolor{red}{30} instances, respectively. Moreover, the library
actually covers the large majority of all possible categories of instances.

>>>>

\begin{table}
{
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{llr}
\toprule
Variables & Convexity & \#\\
\cmidrule(lr){1-3}
%
 \textit{continuous}	& \textit{convex}		&  32 \\[1.2 ex]
 \textit{continuous}	& \textit{nonconvex} 	&  102 \\[1.2 ex]
 \textit{discrete}	& \textit{convex}		&  31 \\[1.2 ex]
 \textit{discrete}	& \textit{nonconvex}	&  288 \\[1.2 ex]
\cmidrule(lr){1-3}
Total		&				& 453\\
%
\bottomrule
\end{tabular}
\caption{Macro classification of the final set of instances}
\label{tab:DDDDD}
}
\end{table}

 The detailed characteristics of the instances are presented in Table
\ref{tab:DD} for \emph{discrete} instances
(\textit{*}\{\textit{B,M,I,G}\}\textit{*}) and in Table
\ref{tab:CC} for \emph{continuous} ones (\textit{*C*}).
For each category, the tables
report in column ``$\#$'' the corresponding number of instances. It can be seen
that the final set well respects the original distribution of the gathered
instances among the different categories. Indeed, the discrete categories
\textit{LMQ} and \textit{QBL} are well represented by {134} and {91}
instances, respectively. Similarly, the continuous categories
\textit{LCQ} and \textit{QCQ} are well
represented by {52} and {30} instances, respectively. Moreover, the library
actually covers the large majority of all possible categories of instances.
